Shaping the Perception of a Robot as a Human-Like Agent by Cognitive Priming

### 2015-11-02 main.tex
New tentative title

\rightheader{Cognitive Priming: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Priming: Impact on the Perception of a Robot}

>>>>

\rightheader{Shaping the Perception of a Robot by Cognitive Priming}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Shaping the Perception of a Robot as a Human-Like Agent by Cognitive
Priming}
